More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-26 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 6 proof in progress

Additionally, we have
$[\alpha'_0.. \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. In other words, $\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0.. \alpha'_n]$. This ensures that $\gamma_{j_0}=[\alpha'_0.. \alpha'_n]$.

@@

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall i \in [0..m].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s_{il}^{\, l\in L} \OTarrow {\tau} s_{(i+1)l}^{\, l\in L}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {t_{l}^{\, l\in L} \OTarrow {\alpha} {t'}_{l}^{\,l\in L}} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..n].\openrule
         {
           \set{\beta^3_i},\Pred^3_i, \Post^3_i}
         {v_{il}^{\, l\in L} \OTarrow {\tau} v_{(i+1)l}^{\, l\in L}} \in \mathcal{T}$ 
\\
where for all $l\in L$:\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
$\\

Moreover, we have for all $p\in[0..n]$:

\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
Also, by Lemma \ref{lem-rel-OT-WOT} this implies the following:\\
$\forall k\! \in\! [0..m']\,\, Q\models{\openrule
			{
				(\beta^1_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_k^{1b}}},  
				{{\Post_k^{1b}}}}
				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(k+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{s_{l}^{l\in L_Q}} \OTarrow {\alpha'_p}
				\ostate{s_{l}'^{l\in L_Q}}}
				}%\]
$
and
$\forall k \in [0..n']\,\, Q\models{\openrule
			{
				(\beta^3_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(k+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Knowing that we have $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$:
Suppose that $Q$ moves in transition $\alpha$, then there is  a matching $p_0$ transition for some $p_0\in[0..n]$. 
\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			(\beta^2_j)^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred^2\land\Pred^{2b}\land \alpha'_{p_0}=\beta^2_{j_0},  
			\Post^2\uplus \Post^{2b}}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
NOTE: And $\beta^2_{j_0}= \beta_{p_0}$.

Moreover, for each:
$\openrule
         {
           \set{\beta_i},\Pred_i, \Post_i}
         {s_i \OTarrow {\tau} s_{i+1}} \in \mathcal{T}$
\qed
\end{proof}

>>>>

Additionally, we have
$[\alpha'_0.. \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0.. \alpha'_n]}$. This ensures that $\gamma_{j_0}=[\alpha'_0.. \alpha'_n]$.

@@

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$\forall p\!\in\![0..m].\openrule
    {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}}\!\in\!\mathcal{T} \wedge
\openrule
         {\set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}\! \in\! \mathcal{T}
\wedge\\
\forall p \in [0..n].\openrule
         {
           \set{\beta^3_p},\Pred^3_p, \Post^3_p}
         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}} \in \mathcal{T}$ 
\\
where for all $l\in L$:\\
$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) l}=s'_i$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=0}^{p-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\bigotimes_{j=0}^{p-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\big)\\
\Post=\bigotimes_{p=0}^{m_2}\Post^3_p\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
$\\
Moreover, we have for all $p\in[0..n]$:
\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
\[Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
				{{\Post'^{2}}}}
				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha'_p}
				\ostate{s_{i}'^{i\in L_Q}}}
				}%\]
\]
We can apply Lemma \ref{lem-compose} on each   $\symb{OT}_p$ of $P$ in the form: 
$P\!\models		
\openrule
    {
       {\beta_p^{p\in J}},\Pred_p,\Post_p   }
         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$ 
\begin{enumerate}
\item If $Q$ moves meaning that we have $Q\!\models		
\openrule
    {
       {\beta_p^{p\in J_Q}},{\Pred_p}\!\!',{\Post_p} \!\!'  }
         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha_p'} \ostate{s^{i\in L}_{(p+1)i}}}$ and having that there exists $j_0\in J$ such that $\alpha'_p=\beta_{j_0}$ then  by Lemma \ref{lem-compose} we obtain:\\ 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
 such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
		{\Post_p}\!\!'$ 
		\item Else $Q$ does not move, i.e. we have: $\ostate{(s_{pi})^{i\in L_Q}} = \ostate{({s}_{(p+1)i})^{i\in L_Q}}$. By Definition \ref{def:Non-ObsTau} we write:

		\[ Q\!\models \openrule
         {
           (j\mapsto\tau),\True,\Id(s_{pi})}
         { \ostate{s^{i\in L}_{pi}} \OTarrow {\tau}\ostate{s^{i\in L}_{pi}}}\]
So we obtain by Lemma \ref{lem-compose}:
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!',  {\Post_p}\!\!' }
         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q}_{(p+1)i}}}\] \\
\end{enumerate}
Therefore we  obtain a series of $m+n$ tau open transitions and a single observable open transition. Thus by Lemma \ref{lem-rel-OT-WOT} that implies we have:
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q}, {\Pred_p}
		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
		{\Post_p}\!\!'}
         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTWeakarrow {\alpha} \ostate{s^{i\in L \uplus L_Q}_{(p+1)i}}}\] 
\qed
\end{proof}
